---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(dplyr)
library(ggplot2)
```

# Transcript of the French presidential TV Debate

This is a provisory transcript of the debate opposing Marine Le Pen and Emmanuel Macron between the two rounds of the 2022 French presidential election (April, 21 2022). 

I plan on using the replay to fill the missing part soon. 

The data was collected live, which explains minor errors in the data: 
  
  + The scraper started collecting data six minutes after the debate started
  + The scraper broke twice and did not collected data for periods of 2 minutes
  + Some sentences are missing, because the subtitle vanished so fast that it could not be collected by the scraper



```{r}
readr::read_rds("data/2022_debat_second_tour.rds") %>%
  dplyr::glimpse()
```


```{r}
readLines("data/2022_debat_second_tour.txt")[1:5]
```


```{r}
readr::read_rds("data/2022_debat_second_tour.rds") %>%
  dplyr::mutate(n_words = stringr::str_count(text, "\\s")) %>% 
  dplyr::group_by(speaker, m5 = lubridate::floor_date(stamp, "10 minutes")) %>%
  dplyr::summarise(sum = sum(n_words)) %>%
  ggplot(aes(x = m5, sum, color = speaker)) +
  geom_line() +
  theme_minimal() +
  labs(x = "Time", y = "Number of spoken words per 5 minutes")

```




